\section{Actions And Actors}\label{sec:actionsAndActors}

The system is governed by a set of rules. These rules define how users are to interact with the system, and how the data is shared among the users. Moreover, once the rules are stored in the blockchain, they can not be altered without broadcasting to all nodes and verified by most of them.
%%% SETUP

\subsection{Setup}\label{sec:Setup}
Setup is the set of actions to configure the application. Setup phase is when a new supply chain is created or an existing one is updated or deleted. Users can also be created, updated and deleted by setup actions. When creating or editing a supply chain, Admin users will define which steps, sub-steps and information that the supply chain flow will contain, and which users from member group is allowed to add info and move asset to each step in the logistics network.

\subsubsection{Administrator}\label{sec:Administrator}
Administrator is the only user in Admin group. This actor has access to all areas of the program and have the same abilities that all other user types (configure, move asset and view flow), but his main responsibility is to configure the application, performing the setup actions. 


%%% DATA INSERTION

\subsection{Data Insertion}\label{sec:DataInsertion}

Data insertion are the actions that will fill the supply chain flow with data. Once a new supply chain is created by the admin user, it is ready to be populated with information. Member and admin users are responsible for perform these actions. In Data Insertion phase users can update information from a specific step and sub-step and move assets depending on the rules applied in the setup phase. The most common actor types in SCM are: Raw material/Producer, Manufacturer, Distributor Wholesaler and Retailer.

%%% VISUALIZATION

\subsection{Visualization}\label{sec:Visualization}

Visualization actions can be performed by any user in the system but its main purpose is to provide to the end user the capability of track the flow off an asset from point of origin to point of consumption.